---
output: github_document
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# **BBcor**: Bayesian Bootstrapping Correlations
[![Build Status](https://travis-ci.org/donaldRwilliams/BBcor.svg?branch=master)](https://travis-ci.org/donaldRwilliams/BBcor)

<!-- badges: start -->
<!-- badges: end -->

The goal of BBcor is to provide an efficient way to obtain samples from the 
posterior distribution of various correlation coefficients:

* Pearson (`method = "pearson"`)

* Spearman (`method = "spearman"`)

* Kendall (`method = "kendall"`)

* Blomqvist (`method = "blomqvist"`; median correlation)

* Polychoric (`method = "polychoric"`)

The method is based on @rubin1981bayesian.

## Installation

<!-- You can install the released version of BBcor from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("BBcor") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("donaldRwilliams/BBcor")
```
## Example: Correlations

This is a basic example which shows you how to solve a common problem, i.e., estimating correlations:

```{r example1}
library(BBcor)
## basic example code

# data
Y <- mtcars[,1:5]

# sample posterior
bb_sample <- bbcor(Y, method = "spearman")


# correlation matrix
bb_sample$cor_mean
```


## Example: Partial Correlations
It is also possible to obtain partial correlations from the object `bb_sample`:

```{r example2}
# convert
pcors <- cor_2_pcor(bb_sample)

# partial correlation matrix
pcors$pcor_mean
```

Note that the objects `bb_sample` and `pcors` include a 3D array with the sampled 
correlation or partial correlation matrices.

## References